Exploring the tree of numerical semigroups

### 2013-10-08 Papier/article.tex
Rewrote figure using tikz

\documentclass[reqno,11pt]{amsart}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{url}
\usepackage{pst-tree}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pgfplots}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{defi}[prop]{Definition}
\newtheorem{nota}[prop]{Notation}
\newtheorem{exam}[prop]{Example}
\newtheorem{lem}[prop]{Lemma}
\newtheorem{fact}[prop]{Fact}

@@

\newcommand{\gr}[1]{{\color{gray} #1}}
%\newcommand{\card}{\#}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\kkp}{{k+1}}
\newcommand{\gen}[1]{\left<#1\right>}
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\newcommand{\NN}{\mathbb{N}}
\renewcommand{\tt}[1]{\texttt{#1}}
\newcommand{\sgnode}[1]{\TR{\bf \left<#1\right>}}
\renewcommand{\ie}{\emph{i.e}}
\DeclareMathOperator{\Irr}{Irr}
\DeclareMathOperator{\App}{App}
\DeclareMathOperator{\card}{card}

@@

 \begin{figure}[htf!]
 \[
 \pstree[,nodesep=3pt]{\sgnode{1}}{
 	\pstree[nodesep=3pt]{\sgnode{2,3} \tlput1}{
 		\pstree[treesep=4pt,nodesep=2pt]{\sgnode{3,4,5} \tlput2}{
 			\pstree[treesep=3pt,nodesep=3pt]{\sgnode{4,5,6,7} \tlput3}{
 				\pstree{\sgnode{5,6,7,8,9} \tlput4}{}
 				\pstree{\sgnode{\gr 4,6,7,9} \tlput5}{}
 				\pstree{\sgnode{\gr 4,\gr 5,7} \trput6}{}
 				\pstree{\sgnode{\gr 4,\gr 5,\gr 6} \trput7}{}					
 			}
 			\pstree[treesep=3pt,nodesep=3pt]{\sgnode{\gr 3,5,7} \tlput4}{
 				\pstree{\sgnode{\gr 3,7,8} \tlput 5}{}
 				\pstree{\sgnode{\gr 3,\gr 5} \trput 7}{}
 			}
 			\pstree[treesep=10pt]{\sgnode{\gr 3,\gr 4} \trput5}{\Tn \Tn \Tn}
 		}
 		\pstree[nodesep=3pt]{~\hspace{-5em}\sgnode{\gr2,5} \trput3}{
 			\pstree[nodesep=3pt]{\sgnode{\gr2,7} \trput5}{
 				\pstree[nodesep=3pt]{\sgnode{\gr2,9} \trput7}{}
 			}
 		}
 	}
 }
 \vspace{-5em}
 \]
\caption{The first five layers of the tree $\mathcal{T}$ of numerical semigroups, corresponding to $\mathcal{T}^{\leq 5}$. A generator of a semigroup is in gray if it is not in $[c(S),+\infty[$. An edge between a semigroup $S$ and its son $S'$ is labelled by  $x$ is $S'$ is obtained from $S$ by removing~$x$, that is $S'=S^x$.}
\label{F:Tree}
\end{figure}

>>>>

\documentclass[reqno,11pt]{amsart}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pgfplots}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{defi}[prop]{Definition}
\newtheorem{nota}[prop]{Notation}
\newtheorem{exam}[prop]{Example}
\newtheorem{lem}[prop]{Lemma}
\newtheorem{fact}[prop]{Fact}

@@

\newcommand{\gr}[1]{{\color{gray} #1}}
%\newcommand{\card}{\#}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\kkp}{{k+1}}
\newcommand{\gen}[1]{\left<#1\right>}
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\newcommand{\NN}{\mathbb{N}}
\renewcommand{\tt}[1]{\texttt{#1}}
\newcommand{\sgnode}[1]{{\bf \left<#1\right>}}
\renewcommand{\ie}{\emph{i.e}}
\DeclareMathOperator{\Irr}{Irr}
\DeclareMathOperator{\App}{App}
\DeclareMathOperator{\card}{card}

@@

 \begin{figure}[htf!]
 % \[
 % \pstree[,nodesep=3pt]{\sgnode{1}}{
 % 	\pstree[nodesep=3pt]{\sgnode{2,3} \tlput1}{
 % 		\pstree[treesep=4pt,nodesep=2pt]{\sgnode{3,4,5} \tlput2}{
 % 			\pstree[treesep=3pt,nodesep=3pt]{\sgnode{4,5,6,7} \tlput3}{
 % 				\pstree{\sgnode{5,6,7,8,9} \tlput4}{}
 % 				\pstree{\sgnode{\gr 4,6,7,9} \tlput5}{}
 % 				\pstree{\sgnode{\gr 4,\gr 5,7} \trput6}{}
 % 				\pstree{\sgnode{\gr 4,\gr 5,\gr 6} \trput7}{}
 % 			}
 % 			\pstree[treesep=3pt,nodesep=3pt]{\sgnode{\gr 3,5,7} \tlput4}{
 % 				\pstree{\sgnode{\gr 3,7,8} \tlput 5}{}
 % 				\pstree{\sgnode{\gr 3,\gr 5} \trput 7}{}
 % 			}
 % 			\pstree[treesep=10pt]{\sgnode{\gr 3,\gr 4} \trput5}{\Tn \Tn \Tn}
 % 		}
 % 		\pstree[nodesep=3pt]{~\hspace{-5em}\sgnode{\gr2,5} \trput3}{
 % 			\pstree[nodesep=3pt]{\sgnode{\gr2,7} \trput5}{
 % 				\pstree[nodesep=3pt]{\sgnode{\gr2,9} \trput7}{}
 % 			}
 % 		}
 % 	}
 % }
 % \vspace{-5em}
 % \]

\[
\begin{tikzpicture}[level distance=2cm, inner sep=2mm,
  level/.style={sibling distance=1.55cm},
%  edge from parent/.style={draw}
  ]
    \node {$\sgnode{1}$}
    child {node {$\sgnode{2,3}$}
      child [sibling distance=4.5cm] {node {$\sgnode{3,4,5}$}
        child {node {$\sgnode{4,5,6,7}$}
          child [sibling distance=2cm]{node {$\sgnode{5,6,7,8,9}$}  edge from parent node [left] {4}}
          child [sibling distance=1.9cm]{node {$\sgnode{\gr 4,6,7,9}$}  edge from parent node [left] {5}}
          child {node {$\sgnode{\gr 4,\gr 5,7}$}  edge from parent node [right] {6}}
          child {node {$\sgnode{\gr 4,\gr 5,\gr 6}$}  edge from parent node [right] {7}}
          edge from parent node [left] {3}
        }
        child{{} edge from parent[draw=none]}
        child{{} edge from parent[draw=none]}
        child {node {$\sgnode{\gr 3,5,7}$}
          child {node {$\sgnode{\gr 3,7,8}$} edge from parent node [left] {5}}
          child {node {$\sgnode{\gr 3,\gr 5}$} edge from parent node [right] {7}}
          edge from parent node [left] {4}
        }
        child {node {$\sgnode{\gr 3,\gr 4}$}
          edge from parent node [right] {5}
        }
        edge from parent node [left] {2}
      }
      child [sibling distance=4.5cm] {node {$\sgnode{\gr2,5}$}
        child {node {$\sgnode{\gr2,7}$}
          child {node {$\sgnode{\gr2,9}$}
            edge from parent node [right] {7}
          }
          edge from parent node [right] {5}
        }
        edge from parent node [right] {3}
      }
      edge from parent node [left] {1}
    }
    ;
  \end{tikzpicture}
  \]
\caption{The first five layers of the tree $\mathcal{T}$ of numerical semigroups, corresponding to $\mathcal{T}^{\leq 5}$. A generator of a semigroup is in gray if it is not in $[c(S),+\infty[$. An edge between a semigroup $S$ and its son $S'$ is labelled by  $x$ is $S'$ is obtained from $S$ by removing~$x$, that is $S'=S^x$.}
\label{F:Tree}
\end{figure}
